Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-26 02_Paper/paper.tex
worked on mm methods section.

Our case of study is an abstraction of an assembly process at the industry. The industry 4.0 demonstration cell is composed by three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200. 
The assembly process done at this demostration cell consist on stacking two disk of different size on the top of each other. The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disk. If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
By considering that malfunctions can occurs during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:

@@

The continous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations. With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner. The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability. This would be an step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.

@@

We compare Support Vector Machines (SVM), Multilinear Perceptrons
\cite{bishop2006pattern} as well as Random forests in the task of
quality prediction.

@@

We work with a total of 132 measurements. Each containing arm and belt data
logs of individual cell runs. 20 samples are set aside at random for testing 
purposes, leaving 112 training samples. The random number generator seed is
set to one in order to ensure the train and test set splits are identical 
for all experiments.

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100.\%
       \end{tabular}
       \caption{Method comparison for our annomaly detection task 
                using the industry demo data test set.}
       \label{tab:class_comp}
\end{table}
Results are shown in table~\ref{tab:class_comp}. For 55 of the total 132 samples
quality measurements indicate a problem. This sets the 
baseline over the entire data set, that would be obtained by simply labeling all samples
as good. Over the entire data set, we require to classify more than 58.3\% of the data correctly.
The test set contains eight incorrect samples. We would therefore expect any naive classifier
to produce a 60\% accuracy, which we have to beat. In Table~\ref{tab:class_comp},
we observe that this is indeed the case for all three approaches evaluated here.
The random forest performed best in this case.

@@

- Connection problem between devices
   - Network connection
   - Device restriction: SIM4000, SIEMENS. 
   - Server Timestamp syncr.
- Interpretation of data: preprocessing
   - What data is relevant?
   - Missing data tags: modifying PLC and robot code to have tags -> key point
        - Without label we cannot use supervised ML methods
- Dataset size
- ML implementation @Moritz

@@

\section*{Acknowledgments}
This project was partly supported by the German and European IKT.NRW
project "`ManuBrain"' 
\DSt{
do we need to include ManuBrain reference here?
}

>>>>

Our case of study is an abstraction of an assembly process at the industry. The industry 4.0 demonstration cell is composed by three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200. 
The assembly process done at this demostration cell consist on stacking two disk of different size on the top of each other. The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disk. If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
By considering that malfunctions can occur during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:

@@

The continuous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations. With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner. The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability. This would be a step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.

@@

We compare Support Vector Machines (SVM), Multilinear Perceptrons
\cite{bishop2006pattern} as well as Random forests in the task of
quality prediction. 
\subsection{Multilinear perceptrons}
These feedforward neural networks typically combine multiple layers
and activation functions. A layer contains a large weight matrix and
a bias vector. To evaluate the layer the input vector must be
multiplied with the weight matrix before the bias vector is added.
Each layer is typically followed by an activation function 
which adds non-linearity to the network graph. Rectified linear units
(ReLUs) are zero for negative inputs leave positive inputs unchanged.
Due to their enormous popularity, we utilize ReLUs here as well.
Since the linear parts of the ReLU and the linear matrix multiplication
are differentiable we can employ gradient descent to train our 
classifier.

\subsection{Support Vector Machines}
Support Vector Machines offer a convex alternative to MLPs \cite{Suykens2002least}.
A convex classifier is guaranteed to converge to a global solution regardless 
of its initialization.

\subsection{Random Forests}

@@

We work with a total of 528 measurements. Each containing arm and belt data
logs of individual cell runs. 50 samples are set aside at random for testing 
purposes, leaving 478 training samples. The random number generator seed is
set to one to ensure the train and test set splits are identical 
for all experiments.

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron (MLP) and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c }
              Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilinear Perceptron & 88 \% \\
              Random Forest          & 98 \%
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
                Random Forest classification on our annomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}
Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples
quality measurements indicate a problem. This sets the 
baseline over the entire data set, which would be obtained by simply labeling all samples
as faulty. Over the test set, we require to classify more than 64\% of the data correctly.
We would therefore expect any naive classifier to produce at least 64\% accuracy, which we have to beat. In Table~\ref{tab:class_comp}, we observe that this is indeed the case for all three approaches evaluated here. We found the random forest performed best followed by the multilinear
perceptron and the support vector machine.

@@

- Connection problem between devices
   - Network connection
   - Device restriction: SIM4000, SIEMENS. 
   - Server Timestamp syncr.
- Interpretation of data: preprocessing
   - What data is relevant?
   - Missing data tags: modifying PLC and robot code to have tags -> key point
        - Without label we cannot use supervised ML methods
- Dataset size
} \\
\textbf{Machine Learning}; careful measurement and  meaningful preprocessing
of our cell-date was key to the successful application of all three algorithms.
Without the labels the problem could not have been framed as a supervised 
classification problem.

@@

\section*{Acknowledgments}
This project was partly supported by the German and European IKT.NRW
project "`ManuBrain"'
